### 2018-09-14 doc/latex/02-Software.tex
Add guide on how to update the included protobuf library

Protocol Buffers\footnote{\url{https://developers.google.com/protocol-buffers/}} is a library used for serializing structured data.
We use it to read and write the population generated by GenGeoPop (see \ref{section:gengeopop}).
It uses an interface description language that describes the structure of the data we want to store, in this case the GeoGrid.
The file that describes how the GeoGrid is structured inside the generated binary file is located at:
\texttt{main/cpp/gengeopop/io/proto/geogrid.proto}
This file is then used to generate the C++ code necessary to read and write our GeoGrid in the structure we provided.
We include this generated code in the project so it's not necessary to install the \texttt{protobuf-c} package\footnote{\url{https://github.com/protobuf-c/protobuf-c}} in order to compile Stride.
These generated source files can be found in the same folder.
If you want to change the structure, for example due to changes in the way the population is generated, you will need to install the previously mentioned package and generate the necessary code again.
To make it easier to do this, we provided a CMake parameter and target that will generate the code and copy it to the source directory respectively.
For this to work, Stride needs to be compiled using the ``\texttt{STRIDE\_GEN\_PROTO=true}" argument.
This will generate the code based on the \texttt{geogrid.proto} file and use that instead of the version included in the source directory.
If you then want to copy this code to the correct location in the source, you can use ``\texttt{make proto}".
If the version of \texttt{protobuf-c} you're using is significantly newer than the one included in this repository, you might also need to update the files stored \texttt{main/resources/lib/protobuf}.

>>>>

Protocol Buffers\footnote{\url{https://developers.google.com/protocol-buffers/}} is a library used for serializing structured data.
We use it to read and write the population generated by GenGeoPop (see \ref{section:gengeopop}).
It uses an interface description language that describes the structure of the data we want to store, in this case the GeoGrid.
The file that describes how the GeoGrid is structured inside the generated binary file is located at:
\texttt{main/cpp/gengeopop/io/proto/geogrid.proto}
This file is then used to generate the C++ code necessary to read and write our GeoGrid in the structure we provided.
We include this generated code in the project so it's not necessary to install the \texttt{protobuf-c} package\footnote{\url{https://github.com/protobuf-c/protobuf-c}} in order to compile Stride.
These generated source files can be found in the same folder.
If you want to change the structure, for example due to changes in the way the population is generated, you will need to install the previously mentioned package and generate the necessary code again.
To make it easier to do this, we provided a CMake parameter and target that will generate the code and copy it to the source directory respectively.
For this to work, Stride needs to be compiled using the ``\texttt{STRIDE\_GEN\_PROTO=true}" argument.
This will generate the code based on the \texttt{geogrid.proto} file and use that instead of the version included in the source directory.
If you then want to copy this code to the correct location in the source, you can use ``\texttt{make proto}".
If the version of \texttt{protobuf-c} you're using is significantly newer than the \texttt{protobuf} included in this repository, you might also need to update the files stored \texttt{main/resources/lib/protobuf}.
At the time of writing, this is done in the following way, although this may be subject to change:
\begin{itemize}
    \item Copy all files from \url{https://github.com/protocolbuffers/protobuf/tree/master/src/google/protobuf} to \texttt{main/resources/lib/protobuf/google/protobuf}.
    \item Copy the \texttt{libprotobuf\_files} and \texttt{libprotobuf\_includes} from \url{https://github.com/protocolbuffers/protobuf/blob/master/cmake/libprotobuf.cmake} and \url{https://github.com/protocolbuffers/protobuf/blob/master/cmake/libprotobuf-lite.cmake}
    \item Remove the prefix \texttt{\${protobuf\_source\_dir}/src/} from these listings.\\
        For example \texttt{\${protobuf\_source\_dir}/src/google/protobuf/any.cc} becomes \texttt{google/protobuf/any.cc}.
    \item Edit the \texttt{CMakeLists.text} at \texttt{main/resources/lib/protobuf} and replace the current values of \texttt{libprotobuf\_files} and \texttt{libprotobuf\_includes} with the ones we just obtained.
\end{itemize}
